---
title: "WUP_04"
author: "Rashonda Weathersby"
date: "Feburary 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
GSSdata <- read.csv(file="GSScsv.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results


`
### Graphical Descriptive Results

   
#### Using ggplot

```{r}
basicCN <- ggplot(GSSdata,aes(x=DEGREE,y=WORDSUM))

basicCN + geom_boxplot()
```
  According to the box plot people with LT high school degrees scored the lowest in the plot with dots outlines on the plot. According to the chart the students with Bachelors and Junior college degrees scored similar, as people with Graduates degrees on average scored the highest. 
  


<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results


```{r}
favstats(WORDSUM~DEGREE,data=GSSdata)
```
The numerical description shows that the Graduates median is at 11 which is the highest score.The Lt High School median is at an 8 which is the lowest of the group. 

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

```{r}
model1 <- aov(WORDSUM~DEGREE,data=GSSdata)
summary.aov(model1)
```


```{r}
model1 <- aov(WORDSUM~DEGREE,data=GSSdata)
summary.aov(model1)
```
```{r}
par(mar= c(3, 15, 2, 2))
plot(TukeyHSD(model1),las=2)
```
 Due to the p value being below one, we cannot conclusively say that there is a different in the hypothesis which makes this a null hypothesis. However according to the tukey model, there are noticeable differences between the degrees however, the p value does not reflect these differences.  
 
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

The question was is there was any significant differences between degrees when it comes to the WORDSUM test score. The hypothesis proved that there is not a significant differences in the the test scores. So the conclusion is null hypothesis. 

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
